### 2022-02-21 title/title.tex
logos, front matter and such
more

op gezag van de Rector Magnificus prof.~dr.~ir.~ [onbekend],

@@

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{l}
    promotoren: Dr.\ A.E.\ Zaidman, Prof.\ dr.\ A.\ van Deursen \\
    copromotor: Dr.\ ir.\ G.\ Gousios
\end{tabular}

@@

@@

\medskip
%% Here you can include the logos of any institute that contributed financially
%% to this dissertation.
\vfill
\begin{center}
    \includegraphics[height=0.5in]{title/logos/tudelft}
    \hspace{2em}
    %\includegraphics[height=0.5in]{title/logos/casimir} \\
    \includegraphics[height=0.5in]{title/logos/nwo}
    \\ \vspace{0.5cm}
    \includegraphics[height=0.5in]{title/logos/ipa}
\end{center}
\vfill

@@

\medskip
\medskip
\noindent The author set this thesis in \LaTeX\xspace using the Libertinus and Inconsolata fonts.

>>>>

op gezag van de Rector Magnificus prof.dr.~V.~Subramaniam,

@@

%% List the promotors (supervisors).
\medskip\noindent
\begin{tabular}{ll}
    promotor: & prof.dr. W. J. Fokkink \\
    copromotoren: & dr. J. C. Blanchette \\
                  & dr. Stephan Schulz
\end{tabular}

@@

\textbf{Should this be filled or skipped as in the case of Alex?}

@@

\medskip
%% Here you can include the logos of any institute that contributed financially
%% to this dissertation.
\vfill
\begin{center}
    \includegraphics[height=0.5in]{title/logos/vulogo}
    \hspace{2em}
    %\includegraphics[height=0.5in]{title/logos/casimir} \\
    \includegraphics[height=0.5in]{title/logos/erclogo}
    \\ \vspace{0.5cm}
    \includegraphics[height=0.5in]{title/logos/ipa}
\end{center}
\vfill

@@

\medskip
\medskip
\noindent The author set this thesis in \LaTeX\xspace using the Minion Pro, Nimbus Sans and Inconsolata fonts.
